### 2022-06-09 manuscript.tex
Merge pull request #224 from SORTEE-Github-Hackathon/RCO-author-name-fix [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6f8258b509eed4946bfc21d796eab05bbae47d1d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6f8258b509eed4946bfc21d796eab05bbae47d1d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2466367408

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c579f2e6dabd3334b02f563bb8ac53bfd042db72/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c579f2e6dabd3334b02f563bb8ac53bfd042db72}{SORTEE-Github-Hackathon/manuscript@c579f2e}
on June 8, 2022.

@@

\textbf{commit}: Commits are snapshots of the development of a project. In Git, versions of files and directories are uniquely identified as ``commits'', allowing one to identify and track modifications line-by-line. Commits can include changes in multiple files and must include a brief commit message describing the changes made. A typical workflow is to make some related changes in files, add a commit message (e.g.~``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (i.e., cloud-based) GitHub \textbf{repository}. \\

@@

\textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (https://github.community/). \\

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6f8258b509eed4946bfc21d796eab05bbae47d1d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6f8258b509eed4946bfc21d796eab05bbae47d1d}{SORTEE-Github-Hackathon/manuscript@6f8258b}
on June 9, 2022.

@@

\textbf{commit}: Commits are snapshots of the development of a project. In Git, versions of files and directories are uniquely identified as ``commits'', allowing one to identify and track modifications line-by-line. Commits can include changes in multiple files and must include a brief commit message describing the changes made. A typical workflow is to make some related changes in files, add a commit message (e.g.~``generate and include fig1 in results''), and after several commits \textbf{push} those commits to the remote (\emph{i.e.}, cloud-based) GitHub \textbf{repository}. \\

@@

\textbf{community}: A forum where GitHub users can ask for advice, offer solutions to questions, and share ideas (\url{https://github.community/}). \\
